Implications of taxonomic bias for microbial differential-abundance analysis

### 2022-08-18 abundance-measurement.Rmd
Increase figure width

```{r error-proportions, out.width = '90%', fig.cap = '(ref:cap-error-proportions)', cache = TRUE}
"figures/illustrations/error-proportions.svg" %>%
  include_svg
```

>>>>

```{r error-proportions, out.width = '100%', fig.cap = '(ref:cap-error-proportions)', cache = TRUE}
"figures/illustrations/error-proportions.svg" %>%
  include_svg
```
